%Abstract

\begin{center}
	{\huge \bf Abstract}
\end{center}
As robotics technology continues to evolve and integrate into various sectors, it brings ethical concerns that must be addressed to ensure responsible development. This paper explores key issues in robotics, focusing on job displacement through automation, moral responsibilities of AI-driven systems, privacy concerns from autonomous data collection, and the misuse of robots in military and surveillance applications. It also examines the challenges of ensuring transparency and accountability in decision-making involving robots, and the implications of granting rights or personhood to autonomous systems. By analyzing these issues, the paper highlights the need for ethical frameworks to guide the safe integration of robotics into society. Additionally, robotics raises significant ethical concerns in areas like well-being, care, and justice. Rescue operations, particularly in disaster settings, introduce further ethical challenges as robots become more common in search and rescue missions. A scoping review identified key ethical themes such as fairness, discrimination, labor replacement, privacy, responsibility, safety, and trust. While the literature on rescue robotics is scant, a proactive approach is universally endorsed. Future research should focus on enriching ethical frameworks to address these concerns.


\vspace{1cm}

\noindent \textbf{Keywords:}  \textit{Robotics, Ethical Concerns, Automation, Autonomous Systems, Ethical Frameworks, Human-Robot Interaction, Technology Ethics.}



\clearpage
\setlength{\headheight}{12pt}